Classless Java

### 2015-11-20 paper/sections/Overview.tex
Commit in conflic, hope is easy to solve

\subsubsection*{\Q@Point3D@ and properties updater}
\Q@Bird@ needs a 3D location, thus first of all we define \Q@Point3D@ and
as follows:
\lstinputlisting[linerange=56-60]{../UseMixinLombok/src/test/TestAnimal.java}% APPLY:linerange=POINT3D

Just to give you a feeling on how much boring code \mixin is generating,  we show the expanded code without then \mixin annotation\footnote{
As you can see, the generated code is very repetitive, writing such code by hand can easily induce bugs, for example a distract programmer may
swap the arguments of one of the many calls of \Q@Point3D.of@.
}.\begin{lstlisting}
interface Point3D extends Point2D{
  Point3D withX(int val);    Point3D withY(int val);    Point3D withZ(int val);
  Point3D with(Point2D val);
  public static Point3D of(int _x, int _y, int _z){
    int x=_x;    int y=_y;    int z=_z;
    return new Point3D(){
      public int x(){return x;}    public int y(){return y;}    public int z(){return z;}
      public Point3D withX(int val){return Point3D.of(val,this.y(),this.z());}
      public Point3D withY(int val){return Point3D.of(this.x(),val,this.z());}
      public Point3D withZ(int val){return Point3D.of(this.x(),this.y(),val);}
      public Point3D with(Point2D val){
        if(val instanceof Point3D){return (Point3D)val;}
        return Point3D.of(val.x(),val.y(),this.z());
        }      };    }  }
\end{lstlisting}
Note how \Q@with-@ methods are automatically refined in their return type, so that code like 
\Q@Point3D p=Point3D.of(1,2,3); p=p.withX(42);@ will be accepted and behave as expected. If the programmer wishes to suppress this behaviour and keep the signature as it was, it is sufficient to redefine the \Q@with-@ methods in the new class repeating the old signature.
Again, the philosophy is that if the programmer provides something directly, \mixin do not touch it.
\Q@with-@ methods (functionally) update a field/property at a time.
This can be inefficient, and sometime hard to maintain.
Often we want to update many fields at the same time, for example using another object as source.
Following this idea, the method \Q@with(Point2D)@ is an example of a (functional) properties updater: 
it takes a certain type and in the current object update all field in that type that match fields in the current type.
The idea is that we want as result something that is still like \Q@this@, but modified to be as much as possible similar to the parameter.
The cast in \Q@with(Point2D)@ is trivially safe since it is guarded by an \Q@instanceof@ test. The idea is that if the parameter is a subtype of the current exact type, then we can just return the parameter, as something that is just ``more'' than \Q@this@.

>>>>

\subsubsection*{\Q@Point3D@ and properties updater}
\Q@Bird@ needs a 3D location, thus first of all we define \Q@Point3D@ and
as follows:
\lstinputlisting[linerange=56-60]{../UseMixinLombok/src/test/TestAnimal.java}% APPLY:linerange=POINT3D
\marco{Fix over: with(Point must be with(Point2D
and it should be after withZ, and on more lines}
Just to give you a feeling on how much boring code \mixin is generating,  we show the expanded code without then \mixin annotation\footnote{
As you can see, the generated code is very repetitive, writing such code by hand can easily induce bugs, for example a distract programmer may
swap the arguments of one of the many calls of \Q@Point3D.of@.
}.\begin{lstlisting}
interface Point3D extends Point2D{
  Point3D withX(int val);    Point3D withY(int val);    Point3D withZ(int val);
  Point3D with(Point2D val);
  public static Point3D of(int _x, int _y, int _z){
    int x=_x;    int y=_y;    int z=_z;
    return new Point3D(){
      public int x(){return x;}    public int y(){return y;}    public int z(){return z;}
      public Point3D withX(int val){return Point3D.of(val,this.y(),this.z());}
      public Point3D withY(int val){return Point3D.of(this.x(),val,this.z());}
      public Point3D withZ(int val){return Point3D.of(this.x(),this.y(),val);}
      public Point3D with(Point2D val){
        if(val instanceof Point3D){return (Point3D)val;}
        return Point3D.of(val.x(),val.y(),this.z());
        }      };    }  }
\end{lstlisting}
Note how \Q@with-@ methods are automatically refined in their return type, so that code like 
\Q@Point3D p=Point3D.of(1,2,3); p=p.withX(42);@ will be accepted and behave as expected. If the programmer wishes to suppress this behaviour and keep the signature as it was, it is sufficient to redefine the \Q@with-@ methods in the new class repeating the old signature.
Again, the philosophy is that if the programmer provides something directly, \mixin do not touch it.
\Q@with-@ methods (functionally) update a field/property at a time.
This can be inefficient, and sometime hard to maintain.
Often we want to update many fields at the same time, for example using another object as source.
Following this idea, the method \Q@with(Point2D)@ is an example of a (functional) properties updater: 
it takes a certain type and in the current object update all field in that type that match fields in the current type.
The idea is that we want as result something that is still like \Q@this@, but modified to be as much as possible similar to the parameter.
The cast in \Q@with(Point2D)@ is trivially safe since it is guarded by an \Q@instanceof@ test. The idea is that if the parameter is a subtype of the current exact type, then we can just return the parameter, as something that is just ``more'' than \Q@this@.
